---
title: "IC_Map"
author: "Linda Menk"
date: "27 11 2020"
output: html_document
---
# Content  

1. Assessment location  
2. Use of risk concept over time  
3. Assessment scale  
4. Model used  
5. Knowledge source: Quantitative data (Modelled data, scenario data, satellite-derived or socio-economic data), qualitative data (Interviews, Workshops, Surveys...), literature (is an extensive literature review specifically mentioned)  

6. Method: Bayesian Networks, Network Analysis, Impact Chains...
7. Assessment scale & purpose (Who are the results directed at?)

8. Challenges per method?

9. Use of scenario/future oriented?

a) Which specific combinations of methods have been used?; 
b) for which purposes? --> Assessment scale  
c) What were the specific challenges of each method?
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(httr)
library(rlist)
library(jsonlite)
library(dplyr)
library(sf)
library(sp)
library(rgdal)
library(tmap)
library(RColorBrewer)
library(ggplot2)
library(ggthemes)
library(tidyverse)
library(scales)


World<-st_read("R:\\100_GeoData\\00_World\\NaturalEarth\\110m_cultural\\ne_110m_admin_0_countries.shp")


Names_1<-c("France","Slovakia","Portugal","Ukraine","Hungary","Uruguay","Mauritania","Ethiopia","Burundi","Somalia","Kenya","Nigeria","Ghana","Mali","Pakistan","Vietnam","Japan","Russia","China","South Korea")
Names_2<-c("Germany","Netherlands","Canada","India","Australia")
Names_3<-c("Spain","Austria","Brazil","United States of America")
Names_8<-c("United Kingdom")
  
World$count<-0
World$count[World$sovereignt %in% Names_1]<- 1
World$count[World$sovereignt %in% Names_2]<- 2
World$count[World$sovereignt %in% Names_3]<- 3
World$count[World$sovereignt %in% Names_8]<- 8

```

```{r map, fig.height=7, fig.width=12}

# Assign continent
Europe<-c("France","Slovakia","Portugal","Ukraine","Hungary","Germany","Netherlands","Spain","Austria","United Kingdom")
Africa<-c("Mauritania","Ethiopia","Burundi","Somalia","Kenya","Nigeria","Ghana","Mali")
Asia<-c("Pakistan","Vietnam","Japan","Russia","China","South Korea","India")
N.America<-c("United States of America","Canada")
S.America<-c("Brazil", "Uruguay")
Oceania<-c("Australia")

World$continent<-NULL
World$continent[World$sovereignt %in% Europe]<- "Europe"
World$continent[World$sovereignt %in% Africa]<- "Africa"
World$continent[World$sovereignt %in% Asia]<- "Asia"
World$continent[World$sovereignt %in% N.America]<- "N.America"
World$continent[World$sovereignt %in% S.America]<- "S.America"
World$continent[World$sovereignt %in% Oceania]<- "Oceania"

World$continent_nr<-NULL
World$continent_nr[World$sovereignt %in% Europe]<- 1
World$continent_nr[World$sovereignt %in% Africa]<- 2
World$continent_nr[World$sovereignt %in% Asia]<- 3
World$continent_nr[World$sovereignt %in% N.America]<- 4
World$continent_nr[World$sovereignt %in% S.America]<- 5
World$continent_nr[World$sovereignt %in% Oceania]<- 6

#Remove all other countries from the dataset
ed_exp4 <- subset(World, count != 0)


#Make dataframe from remaining countries
spatial<-data.frame("sovereignt"=ed_exp4$sovereignt, "count"=ed_exp4$count, "continent"=ed_exp4$continent, "cont_nr"=ed_exp4$continent_nr)
#Remove duplicates
spatial <- spatial[-c(10, 29), ]

#Europe & World
#Europe<-data.frame("Europe",3,"Overarching",7)
#names(Europe)<-c("sovereignt","count","continent","cont_nr")
#spatial<-rbind(spatial,Europe)

#Global<-data.frame("Global",3,"Overarching",7)
#names(Global)<-c("sovereignt","count","continent","cont_nr")
#spatial<-rbind(spatial,Global)


#write.csv(spatial, "spatial.csv", row.names = FALSE)
#getwd()
spatial_2 <- read.csv("spatial.csv")

spatial_2

#Make the plot
map<-ggplot(spatial_2,aes(x=count, y=reorder(sovereignt, count), fill = continent))+
  geom_bar(stat="identity", width=0.7)+
  ggtitle("RQ 1.1 Assessment location")+xlab("")+ylab("")+
  scale_fill_wsj() +
  theme_minimal() +
  facet_grid(spatial_2$cont_nr~., scales ="free",space="free")+
  labs(fill = " ") +
  theme(strip.text.y=element_blank()) +
  theme(legend.position="bottom") +
  scale_x_continuous(breaks=0:10)
  
map



```

```{r risk}

AR4<-"Vulnerability (Adaptive Capacity + \n Exposure + Sensitivity) + Hazard"
AR5<-"Vulnerability + \nExposure + \nHazard"
None<-"Other/\nNone mentioned"
NAP<-"Not applicable"
Oth<-"Other"

#Times risk concept
types_df<-data.frame(
  type=c(AR4, AR5, NAP, Oth, None),
  count=c(9,11,6,3,9)
  )

p<-ggplot(data=types_df, aes(x=count, y=type)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=count), vjust=1.6, color="white", size=3.5, nudge_x = -1)+
 ggtitle("Assessment scale")+xlab("Number of studies")+ylab(" ")
p

#Times per year
years_df<-data.frame(year=as.factor(c(2010,2011,2012,2013,2014,2015,2016,2017,2018,2019)),
                     times=c(1,0,1,2,5,5,4,2,13,5))
p<-ggplot(data=years_df, aes(x=year, y=times)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=times), vjust=1.6, color="white", size=3.5, nudge_x = 0,nudge_y=0)+
 ggtitle("Articles per year")+xlab("Number of articles")+ylab("Year")+theme_solarized() 
p

df <- data.frame(
  group = c(AR4, AR5, AR4, None, NAP, AR5, None, None, None, AR5, None, None, AR4, None, None, None, None, AR5, NAP, None, NAP, NAP, AR5, NAP, AR5, NAP, None, AR5, AR5, AR4, AR4, AR5, AR4, AR4, AR5, AR4, AR4, AR5, None, None, AR4, None, None, None, None),
  value = as.factor(c(2015, 2018, 2018, 2014, 2016, 2018, 2015, 2018, 2018, 2017, 2018, 2018, 2012, 2018, 2015, 2018, 2010, 2016, 2017, 2014, 2019, 2013, 2015, 2019, 2018, 2019, 2013, 2019, 2016, 2014, 2014, 2018, 2014, 2016, 2018, 2018, 2015, 2019, 2018, 2014, 2017, 2018, 2019, 2016, 2018))
  )
df

library(ggplot2)

theme_update(plot.title = element_text(hjust = 0.5))

#Risk conceptualisation plot
p<-ggplot(data=df, aes(x=value, y=group)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -1)+
 ggtitle("Risk conceptualisation")+xlab("Number of studies")+ylab(" ")
p



ggplot(df, aes(x = value)) +
    geom_bar(stat="count")
#-----------
tbl <- with(df, table(group,value))


df<-data.frame(tbl)

p<-ggplot(df,aes(factor(value), Freq, fill = group))+geom_bar()+ggtitle("Definitions over time")+xlab("Definition")+ylab("Usage per year")

p<-ggplot(df,aes(x = value, y = Freq, fill = group))+geom_bar(stat="identity", width=0.5)+ggtitle("RQ 1.4 Risk concepts over time")+xlab(" ")+ylab("Number of articles")+
  scale_fill_wsj() +
  theme_minimal() +
  theme(legend.position="bottom") +
  labs(fill = "Risk concept")

p


# Stacked
ggplot(df, aes(fill=value, x=value)) + 
    geom_bar(position="stack", stat="identity", width = 1)
# Horizontal bar plot
#p + coord_flip()

```

```{r scale}
scale <- data.frame(
  group = c("Global","Continental","Multi-national","National","Sub-national","Urban area/City","Local","Infrastructure"),
  value = c(3,3,2,13,11,7,3,2)
  )

p<-ggplot(scale,aes(x=value, y=reorder(group,value)))+geom_bar(stat="identity", width=0.5)+ggtitle("Assessment scale")+xlab("Times mentioned")+ylab("")+
  scale_fill_wsj() +
  theme_minimal() +
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -1, nudge_y = +0.3)

p
# Horizontal bar plot
#p + coord_flip()

```

```{r risk}
risk <- data.frame(
  group = c("Sensitivity, Adaptive capacity", "IPCC AR5/DRR","Not specified","Other"),
  value = c(8, 9, 16, 6)
  )
head(risk)

library(ggplot2)

theme_update(plot.title = element_text(hjust = 0.5))

p<-ggplot(data=risk, aes(x=value, y=group)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -1)+
 ggtitle("Conceptionalisation of risk")+xlab("Number of studies")+ylab(" ")
p


# Horizontal bar plot
#p + coord_flip()

```

```{r model}
model <- data.frame(
  group = c("Economic quantification", "Impact Chain","Network Analysis","SD/CLD/Scenario based","Other"),
  value = c(7, 12, 5, 7,8)
  )
head(model)

library(ggplot2)

theme_update(plot.title = element_text(hjust = 0.5))

p<-ggplot(data=model, aes(x=value, y=group)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -1)+
 ggtitle("Used modelling techniques")+xlab("Number of studies")+ylab(" ")
p


# Horizontal bar plot
#p + coord_flip()

```
```{}
Network Analysis, 
Network Analysis, 
Structural Decomposition Analysis with Network Theory
Network Theory in GIS with literature and government reports
Multiplex Network Analysis
Two-dimensional self-organizing neural network
Network flowchart (result?)
Network map (result?)

Graph based approach 
Directed graph 
Deterministic graph

Bayesian Networks
Bayesian Network Analysis

System dynamics model
Hydrologic and system dynamics model
Hydrological model
Simulation-based approach
Input-output tables
Agent based model

Standardized comparative analysis

Causal chain, 
Causal chain,
Impact Chain (4x)
Meta-analysis, Scenario development, Causal chains/loops
Causal Loop Diagram
Scenario planning process, Causal Loop Diagramming process
Causal Chains/Loops based on Driver-Pressure-State-Impact-Response framework
Co-creation process
Focus group method


Index methodologies
Indicator based Vulnerability Assessment
Climate vulnerability indicators
Multiplicative framework based on simple utility function
Fuzzy cognitive map
Fuzzy risk raster map (result)
Fuzzy logic algorithm

Model
Scour risk model
Single system model and system-of-systems model
Statistical and process based models
Impact assessment models and uniform multi-sectoral computable general equilibrium model
MRIA model (input-output based model)
MRIO model
IAP model (CLIMSAVE integrated assessent platform)
SWAT model
HAZUR tool
Morans I
Cost-benefit analysis
Modelling framework

Sensitivity analysis


```

```{r knowledge}
knowledge <- data.frame(
  group = c("Participatory (incl. expert opinion, \nstakeholder experience, surveys)", "Literature","Existing models","Statistical, quantitative \ndata analysis"),
  value = c(19, 17, 7, 17)
  )

p<-ggplot(knowledge,aes(x=value, y=group))+geom_bar(stat="identity", width=0.5)+ggtitle("Knowledge acquisition method")+xlab("Times mentioned")+ylab("")+
  scale_fill_wsj() +
  theme_minimal() +
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -1, nudge_y = +0.18)

p
# Horizontal bar plot
#p + coord_flip()

```
```{r Treemap, fig.height=5}



hazard<-data.frame(names=c("Changed precipitation patterns",
                           "Changed temperature patterns",
                           "Rapid onset events",
                           "Heatwave",
                           "Cold spell",
                           "Sea Level Rise",
                           #"Coastal erosion",
                           "Storm surges/(Coastal) floods",
                           "Storm/wind, heavy precipitation, snow",
                           "(Coastal) erosion/landslide",
                           "Water scarcity",
                           "Water quality deterioration",
                           "Salinization",
                           "Drought",
                           "Desertification/forest dieback",
                           "Overarching w/o specification"),
                   value=c(3,3,4,7,3,2,22,9,9,2,2,1,11,2,11),
                   level=as.character(c(20,20,10,1,1,2,0,0,0,1,1,0,1,1,5)))

#Make the plot
map<-ggplot(hazard,aes(x=value, y=reorder(names,value), fill=level))+geom_bar(stat="identity", width=0.7)+ggtitle("RQ 1.3. Assessed hazards/climate impacts")+xlab("")+ylab("")+
  scale_fill_wsj() +
  theme_minimal() +
  facet_grid(hazard$level~., scales ="free",space="free")+
  labs(fill = " ") +
  theme(legend.position = "none",strip.text.y=element_blank())
  
map
```


```{r selection process, fig.width=9,fig.height=7}
selection <- data.frame(
                            stringsAsFactors = FALSE,
                                 check.names = FALSE,
                          `Risk.assessment?` = c(0,1,1,
                                                 0,0,1,0,1,0,1,
                                                 1,0,1,0,0,0,1,1,
                                                 1,1,1,1,1,1,0,0,
                                                 1,0,0,0,0,1,0,0,
                                                 0,0,0,1,0,1,0,
                                                 0,0,0,1,1,0,0,0,
                                                 0,0,0,0,0,0,0,1,
                                                 0,0,0,0,1,1,1,1,
                                                 1,0,0,0,0,0,0,
                                                 1,0,0,0,1,0,0,0,
                                                 0,0,1,0,0,0,0,0,
                                                 0,0,0,0,1,0,1,0,
                                                 0,1,0,0,0,0,1,
                                                 0,0,1,0,0,1,0,0,
                                                 1,0,1,1,0,1,1,1,
                                                 1,0,1,0,1,0,0,1,
                                                 0,1,0,0,1,0,
                                                 1,1,0,0,1,1,1,0,
                                                 1,0,1,0,1,0,0,1,
                                                 0,1,0,0,1,0,0,
                                                 1,0,0,0,1,0,1,
                                                 1,1,0,1,1,1,0,0,
                                                 1,0,1,0,0,0,1,0,
                                                 0,1,0,0,1,1,0,1,
                                                 1,0,0,0,0,0,0,
                                                 1,1,0,1,1,1,0,0,
                                                 0,0,0,1,1,0,0,0,
                                                 0,0,1,0,0,1,1,0,
                                                 1,1,1,1,0,1,0,
                                                 0,0,1,0,0),
                     `Systemic.perspective?` = c(0,1,
                                                 0,1,0,1,0,1,
                                                 0,0,1,1,1,1,
                                                 0,0,1,1,1,1,1,
                                                 1,0,1,0,0,0,
                                                 1,1,1,0,1,1,
                                                 1,0,0,0,1,1,
                                                 1,0,0,1,1,0,
                                                 0,0,0,0,1,1,0,
                                                 1,1,0,1,1,1,
                                                 0,0,1,1,1,1,
                                                 1,1,1,0,0,0,
                                                 0,0,1,0,0,0,
                                                 0,1,0,1,1,0,1,
                                                 0,0,0,0,0,1,
                                                 0,0,0,1,0,1,
                                                 0,0,1,1,1,0,
                                                 0,1,0,0,1,0,
                                                 1,0,0,0,1,0,1,
                                                 0,1,0,1,1,1,
                                                 1,0,0,1,0,1,
                                                 1,1,1,1,1,
                                                 1,0,1,1,1,0,1,
                                                 0,0,0,1,1,1,
                                                 1,0,1,0,0,
                                                 0,1,1,0,0,0,
                                                 0,0,0,0,0,1,0,
                                                 1,1,1,1,1,1,
                                                 1,0,1,1,0,1,
                                                 0,0,0,1,0,0,
                                                 1,1,1,1,1,0,
                                                 1,1,1,0,1,1,1,
                                                 0,0,1,1,1,1,
                                                 1,0,0,1,0,0,
                                                 1,1,1,1,1,0,
                                                 0,1,1,1,1,1,
                                                 0,1,1,1,1,0,1,
                                                 1,0,0,0,0,1),
  `CC.context?.(environmenta.aspect.of.cc)` = c(1,1,0,
                                                 0,1,1,1,0,1,1,
                                                 1,0,1,1,1,1,1,1,
                                                 1,1,1,1,1,1,1,1,
                                                 1,1,0,0,1,1,1,1,
                                                 1,1,1,1,0,1,1,
                                                 0,0,1,0,1,1,1,1,
                                                 1,0,1,1,0,0,1,1,
                                                 1,0,1,1,1,1,1,1,
                                                 1,1,1,0,0,1,1,
                                                 1,0,1,1,1,1,0,1,
                                                 0,1,1,0,1,1,1,1,
                                                 0,1,1,0,1,1,1,1,
                                                 0,1,1,1,1,0,1,
                                                 1,0,1,0,1,1,1,1,
                                                 0,0,1,1,1,1,1,1,
                                                 1,1,1,1,1,1,1,1,
                                                 1,0,1,1,1,1,
                                                 1,1,1,0,1,1,1,1,
                                                 1,0,1,1,0,0,1,1,
                                                 0,1,1,1,0,1,1,
                                                 1,1,1,0,1,0,1,
                                                 1,1,1,1,1,1,1,1,
                                                 1,0,0,1,0,1,1,1,
                                                 0,1,1,1,1,1,0,1,
                                                 1,1,0,1,1,1,1,
                                                 1,0,1,1,1,1,0,1,
                                                 1,1,1,1,1,1,1,1,
                                                 1,1,1,1,1,1,1,1,
                                                 1,1,1,1,1,1,1,
                                                 0,1,1,1,1),
                               `Conceptua?` = c(0,0,0,
                                                 0,1,0,1,1,0,0,
                                                 0,0,0,0,1,0,1,0,
                                                 0,0,0,0,0,0,1,1,
                                                 0,0,1,0,1,0,1,1,
                                                 1,1,0,0,0,1,0,
                                                 0,0,0,0,0,1,0,0,
                                                 0,0,1,0,0,0,1,0,
                                                 0,1,1,0,1,0,0,0,
                                                 0,0,1,0,1,1,0,
                                                 0,1,0,1,1,0,0,0,
                                                 0,0,0,0,0,1,1,0,
                                                 0,0,1,1,0,0,0,0,
                                                 0,0,0,0,1,0,0,
                                                 0,0,0,0,0,1,1,1,
                                                 0,0,0,0,1,0,0,0,
                                                 1,0,0,1,0,1,0,0,
                                                 0,0,0,0,1,0,
                                                 0,0,1,0,0,1,0,0,
                                                 0,0,0,1,0,0,0,0,
                                                 0,0,1,0,0,0,0,
                                                 0,1,0,0,0,1,0,
                                                 0,0,0,0,0,0,1,0,
                                                 0,0,0,0,0,0,0,0,
                                                 0,0,0,0,0,0,0,0,
                                                 0,0,0,1,0,1,1,
                                                 0,0,0,0,1,0,0,1,
                                                 0,1,0,0,0,0,0,0,
                                                 1,0,0,0,1,0,0,0,
                                                 0,0,0,0,0,0,0,
                                                 0,1,0,1,0)
)

selection_id <- cbind(ID = 1:nrow(selection), selection)


selection_ra <- round(sum(selection$`Risk.assessment?`)/232*100)
selection_sp <- round(sum(selection$`Systemic.perspective?`)/232*100)
selection_cc <- round(sum(selection$`CC.context?.(environmenta.aspect.of.cc)`)/232*100)
selection_cr <- round(sum(selection$`Conceptua?`)/232*100)

group <- c("Risk assessment","Systemic prespective","Climate change context","Conceptual/Review")
value <- c(selection_ra, selection_sp, selection_cc, selection_cr)

data <- data.frame(group, value)


theme_update(plot.title = element_text(hjust = 0.5))

p<-ggplot(data=data, aes(x=value, y=reorder(group, value))) +
  geom_bar(stat="identity")+
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -4)+
 ggtitle("Articles fitting inclusion/exclusion criteria")+xlab("% of articles")+ylab(" ")
p

#----Stacked Bar Chart

selection_id$`Risk.assessment?`<-as.factor(selection_id$`Risk.assessment?`)
selection_id$`Systemic.perspective?`<-as.factor(selection_id$`Systemic.perspective?`)
selection_id$`CC.context?.(environmenta.aspect.of.cc)`<-as.factor(selection_id$`CC.context?.(environmenta.aspect.of.cc)`)
selection_id$`Conceptua?`<-as.factor(selection_id$`Conceptua?`)

a <- dplyr::count(selection_id, `Risk.assessment?`)
b <- dplyr::count(selection_id, `Systemic.perspective?`)
c <- dplyr::count(selection_id, `CC.context?.(environmenta.aspect.of.cc)`)
d <- dplyr::count(selection_id, `Conceptua?`)



kat <- c(1,1,2,2,3,3)
value <- c(a$n[1], a$n[2], b$n[1], b$n[2], c$n[1], c$n[2])
YN <- c("NO", "YES", "NO", "YES", "NO", "YES")
criteria <- c("Human-centered risk, \n vulnerability or \nimpact assessment", "Human-centered risk, \n vulnerability or \nimpact assessment",  "Dynamics and causal \nstructures behind risk","Dynamics and causal \nstructures behind risk", "Climate change \ncontext", "Climate change \ncontext")

stack_in <- data.frame(kat, value, YN, criteria)
#library(data.table)


inclusion <- ggplot(stack_in, aes(fill = YN, x=criteria, y=value, kat)) +
  labs(title = "Step 3a: Included/Excluded on abstract", subtitle = "Inclusion criteria") +
  geom_bar(position = "fill", stat = "identity") +
  xlab("Inclusion/Exclusion criteria")+
  ylab("") +
  labs(fill = " ") +
  theme(strip.text.y=element_blank()) +
  #scale_x_discrete(labels = criteria) +
  scale_y_continuous(labels = percent) +
  #geom_text(aes(label=value)) +
  scale_fill_wsj(name="Has this criterion been met?") +
  theme_minimal() +
  theme(legend.position="bottom")

# exclusion-----
kat <- c(4,4)
value <- c( d$n[1], d$n[2])
YN <- c("NO", "YES")
criteria <- c("Concept or \nReview", "Concept or \nReview")

stack_ex <- data.frame(kat, value, YN, criteria)

exclusion <- ggplot(stack_ex, aes(fill = YN, x=criteria, y=value, kat)) +
  #ggtitle("Abstract screening results") +
  labs(subtitle = "Exclusion criteria") +
  geom_bar(position = "fill", stat = "identity") +
  xlab("Inclusion/Exclusion criteria")+
  ylab("") +
  labs(fill = " ") +
  theme(strip.text.y=element_blank()) +
  #scale_x_discrete(labels = criteria) +
  scale_y_continuous(labels = percent) +
  #geom_text(aes(label=value)) +
  scale_fill_wsj() +
  theme_minimal() +
  theme(legend.position="bottom")

exclusion
library(png)
library(patchwork)
#my_image <- readPNG("R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP1\\T1_3\\Manuscript\\01_Review\\NewFigures\\Screening_results_final_v2.PNG")

library(patchwork)
inclusion + exclusion + #inset_element(p = my_image,
                                      #left = 0,
                                      #bottom = 0,
                                      #right= 1,
                                      #top=1) +
  plot_layout(widths = c(2.5,1))
 

```

```{r inclusion points,  fig.width=12,fig.height=7}
selection_id2 <-cbind(ID = 1:nrow(selection), selection)

row_wise_sum <- selection_id2 %>% mutate(row_wise_sum = rowSums(.[2:4]))

# Coerce to factor to count the number of occurrences
row_wise_sum$row_wise_sum <- as.factor(row_wise_sum$row_wise_sum)

# To filter where all the inclusion criteria are met
traffic_light <- dplyr::count(row_wise_sum,row_wise_sum)

# To filter where the inclusion criteria are met and additionally the exclusion criteria is met. 
add_lit <- filter(row_wise_sum, row_wise_sum == '3' & `Conceptua?` == '1')

#----
traffic_light$names <- c("0", "1", "2", "3") # Because I filtered 7 additional papers that fit all inclusion and the exclusion criteria

#kat <- c(1,1,1,1)
#value <- c(traffic_light$n[1],traffic_light$n[2], traffic_light$n[3], traffic_light$n[4])
#number <- c("0","1","2","3")
#criteria <- c("Concept or \nReview", "Concept or \nReview")


#stack_traffic <- data.frame(kat, value, number)

traffic_light_plot <- ggplot(traffic_light,aes(x="", y=n ,fill= row_wise_sum)) +
  geom_bar(stat = "identity", width =1) +
  coord_polar("y", start = 0) +
  #scale_fill_discrete(name="Times...", labels = traffic_light$names) +
  scale_fill_wsj(name="Criteria met", labels = traffic_light$names) +
  theme_fivethirtyeight() +
  labs(subtitle = "How many abstracts met 0, 1, 2 or 3 inclusion criteria?", caption = "232 abstracts were screened. Only those which fit all three inclusion criteria were added \nto the assessed literature. This was true for 68 articles. 7 of them additionally fit the exclusion criteria, namely that they \nwere either conceptual papers or review papers. However, as these 7 papers are closely related to this topic, \nthey were considered in the introduction of the paper as related papers. As for the quantitative analysis, 61 papers remained.")  
  

library(patchwork)
patch <- inclusion + exclusion +
  plot_layout(widths = c(2.5,1,1))

inclusion + exclusion + traffic_light_plot + 
  plot_layout(widths = c(3,1,2.5))
```

```{r }
library(data.table)

ops.mat <-
  matrix(c(392,  114,  250, 115, 115,  78,
           2349, 560,  428, 286, 226, 173,
           4037, 1215, 817, 879, 479, 337,
           966,  592,  142, 256,  90, 407,
           1,1,1,1,1,1,
           1,1,1,1,1,1
           ),
         nrow=6, byrow=TRUE)

project.node.totals <- c(28047, 79005, 140853, 29529)

rownames(ops.mat) <- c("Modelled data","Historical data", "Other existing data", "Expert Interview/Survey/Workshop", "Stakeholder Interview/Survey/Workshop", "Extensive literature review")
colnames(ops.mat) <- c("Impact \nChains","Simulations","Graph/\nNetwork-based","Models","Qualitative\n Evaluation","Fuzzy \nMethods")

scale.max.1 <- function(x) x / max(x)
ops.rate.mat <- scale.max.1(apply(ops.mat, 2, '/', project.node.totals))

ops.rate.df <- data.frame(melt(ops.rate.mat, varnames=c("parser", "op"), value.name = "rate"))
ggplot(data=ops.rate.df, aes(op, parser)) + geom_point(aes(size = rate))


colors <- pals::parula(10)[c(1,4,7,9)]

 ggplot(ops.rate.df, aes(op, parser)) +  ggtitle("Methods and source information") +
                   geom_point(colour = colors[[1]], aes(size = rate)) +
  scale_fill_wsj() +
  theme_fivethirtyeight() 
```
```{r Scale and Sector, fig.width=8}




scale_sector <- data.frame(
  stringsAsFactors = FALSE,
                           Scale = c("Local","Sub-national",
                                       "National","Sub-national","Urban area/City",
                                       "National","National","Sub-national",
                                       "National","Sub-national","Sub-national",
                                       "National","Sub-national",
                                       "Transnational","Sub-national","Global",
                                       "Local","Sub-national","Sub-national",
                                       "Urban area/City","Local",NA,
                                       "Global","Sub-national","Transnational",
                                       NA,"Transnational","Local",
                                       "Sub-national","Sub-national",
                                       "Urban area/City","Transnational",
                                       "Local","Transnational","Sub-national",
                                       "Sub-national","Sub-national","National",
                                       "National","Sub-national",
                                       "Transnational","Local","Urban area/City",
                                       "Transnational","Urban area/City",NA,
                                       "National"),
                           Sector = c("Critical Infrastructure","Multiple",
                                       "Multiple","Agriculture, Food Security","Environment, Urban living",
                                       NA,"Water","Water","Water",
                                       "Environment, Urban living","Water","Critical Infrastructure",
                                       "Water",NA,"Agriculture, Food Security","Multiple",
                                       "Critical Infrastructure","Water",
                                       "Environment, Urban living","Critical Infrastructure",
                                       "Critical Infrastructure","Agriculture, Food Security",
                                       "Agriculture, Food Security","Multiple","Multiple","Water",
                                       "Multiple",NA,NA,"Water",
                                       "Critical Infrastructure","Agriculture, Food Security",
                                       "Critical Infrastructure","Multiple",NA,NA,
                                       "Critical Infrastructure",NA,"Agriculture, Food Security",
                                       "Agriculture, Food Security","Water",
                                       "Critical Infrastructure","Agriculture, Food Security","Agriculture, Food Security",NA,
                                       "Environment, Urban living","Environment, Urban living")
                )




theme_update(plot.title = element_text(hjust = 0.5))

#-----------
xx <- with(scale_sector, table(Scale, Sector))
scale_sector<-data.frame(xx)

library(plyr)
scale_sector.count = count(scale_sector)
positions = c("Global","Transnational","National","Sub-national","Urban area/City","Local")
p<-ggplot(scale_sector,aes(x = Scale, y = Freq, fill = Sector))+
  geom_bar(stat="identity", width=0.5)+
  ggtitle("RQ 1.2 Assessment scale and assessed sector")+xlab(" ")+ylab("Number of articles")+
  scale_fill_wsj() +
  theme_minimal() +
  theme(legend.position="bottom") +
  labs(fill = "Sector", subtitle = "* Multiple answers possible")+
  scale_x_discrete(limits = positions)

p



```
```{r methods and information sources, fig.width=7, fig.height=6}


library(ggmosaic)

# Set up the vectors                           
methods <- c("Impact Chains (8)","Qualitative models of \ncause and effect (17)","Quantitative models \nand simulations (28)")
information <- c("Extensive \nliterature review","Modelled data","Measured or \nsurveyed data","Experts/\nStakeholders")

# Create the comporessed data frame
df <- expand.grid(methods, information, stringsAsFactors = TRUE)
#df$value <- c(16,83,100,100,47,11,17,76,17,53,64,10)    
df$value <- c(1,8,5,5,2,15,7,3,18,7,13,3)
df.expanded <- df[rep(row.names(df), df$value), 1:2]

#		    Lit	Model	Survey	Exp
#IC	        1 	5	6	7
#Other qual	8	2	3	13
#Simul	      5	15	18	3


#Plot the Data
ggplot(data = df.expanded) +
  geom_mosaic(aes(x = product(Var2,Var1), fill = Var2)) + 
  ggsave("mosaic.png") +
  scale_fill_wsj() +
  theme_minimal() +
  theme(legend.position="bottom") +
  labs(title="RQ 2 Methods and information sources", fill = "Information \nsource", subtitle = "One article can have multiple information sources and methods. \nThe bar widths are scaled according to the number of articles per category.", y="",x="") +
  geom_text(data = layer_data(last_plot(), 1) %>% filter(.wt > 0),
             aes(x = (xmin + xmax) / 2,
                 y = (ymin + ymax) / 2,
                 label = .wt), color="white", size=4.5)


```
```{r challenges and opportunities, fig.height=8, fig.width=12}

IC_title <- "Impact Chains"
Qual_title <- "Qualitative models of \ncause and effect"
Quan_title <- "Quantitative models \nand simunlations"
label <- c("Challenges","Opportunities")
             
           
categories <- c("Stakeholder involvement","Cause effect identification","Communication of concepts \nand results","Quantification of system \nelements and interrelations", "Data gaps","Evaluation and \validation options")

#IC____________________________
# Create the comporessed data frame
df <- expand.grid(label, categories, stringsAsFactors = TRUE)

df$value <- c(4,4,2,2,2,5,0,1,4,0,0,1)
df.expanded <- df[rep(row.names(df), df$value), 1:2]

#Plot the Data
ic <- ggplot(data = df.expanded) +
  geom_mosaic(aes(x = product(Var2,Var1), fill = Var2)) + 
  ggsave("mosaic.png") +
  scale_fill_wsj() +
  theme_minimal() +
  theme(legend.position="bottom") +
  labs(title="RQ 3 Challenges and opportunities of different methods", fill = "Topic", subtitle = "One article can have multiple challenges, opportunities and methods. \nThe bar widths are scaled according to the challenges/opportunities ratio.", y="",x=IC_title) +
  theme(title=element_text(size=17),plot.subtitle=element_text(size=14), axis.text=element_text(size=13),
        axis.title=element_text(size=13), legend.text = element_text(size=13)) +
  geom_text(data = layer_data(last_plot(), 1) %>% filter(.wt > 0),
             aes(x = (xmin + xmax) / 2,
                 y = (ymin + ymax) / 2,
                 label = .wt), color="white", size=5)

#Qualitative____________________________________
df <- expand.grid(label, categories, stringsAsFactors = TRUE)

df$value <- c(6,5,1,6,3,12,2,1,1,2,2,3)
df.expanded <- df[rep(row.names(df), df$value), 1:2]

#Plot the Data
qual <- ggplot(data = df.expanded) +
  geom_mosaic(aes(x = product(Var2,Var1), fill = Var2),show.legend = FALSE) + 
  ggsave("mosaic.png") +
  scale_fill_wsj() +
  theme_minimal() +
  scale_y_productlist(labels = NULL) +
  labs( y="",x=Qual_title) +
  theme(axis.title=element_text(size=13),axis.text=element_text(size=13)) +
  geom_text(data = layer_data(last_plot(), 1) %>% filter(.wt > 0),
             aes(x = (xmin + xmax) / 2,
                 y = (ymin + ymax) / 2,
                 label = .wt), color="white", size=5)

#Quantitative________________________________________
df <- expand.grid(label, categories, stringsAsFactors = TRUE)

df$value <- c(4,4,5,7,3,13,6,5,4,2,8,4)
df.expanded <- df[rep(row.names(df), df$value), 1:2]

#Plot the Data
quan <- ggplot(data = df.expanded) +
  geom_mosaic(aes(x = product(Var2,Var1), fill = Var2),show.legend = FALSE) +
  ggsave("mosaic.png") +
  scale_fill_wsj() +
  theme_minimal() +
  scale_y_productlist(labels = NULL) +
  labs( y="",x=Quan_title) +
  theme(axis.title=element_text(size=13),axis.text=element_text(size=13)) +
  geom_text(data = layer_data(last_plot(), 1) %>% filter(.wt > 0),
             aes(x = (xmin + xmax) / 2,
                 y = (ymin + ymax) / 2,
                 label = .wt), color="white", size=5)
  
library(patchwork)

ic + qual + quan +
  plot_layout(widths = c(1,1,1))
```


```{r flowchart}
library(DiagrammeR)
grViz("
digraph test {
  node[shape = box]
  Scopus;Web of Science
  
  node[shape = circle]
  262; 40
  
  # add edge statement
  Scopus -> 262; Web of Science ->40
}
")

```

```{r stef}
library(ggplot2)

#load polygons
library(sf)
Hitze_P1rcp45q05 <- st_read("R:\\02_PROJECTS\\01_P_330001\\PKF330001_02_HotSpots\\01_Data\\Daten-vom-20201013\\Hotspots_Karten\\Index_shapefiles\\Hitzebelastung_P1rcp45q05_SmoothSBG_1.shp")
plot(Hitze_P1rcp45q05)
Hitze_P1rcp45q05_density <- density(Hitze_P1rcp45q05$Hitze_P1rc)
plot(Hitze_P1rcp45q05_density)

ggplot(Hitze_P1rcp45q05) +
  geom_density(aes(Hitze_P1rc)) +
  geom_vline(aes(xintercept = min(Hitze_P1rc)), color = 'red') +
  geom_vline(aes(xintercept = mean(Hitze_P1rc)), color = 'blue') +
  geom_vline(aes(xintercept = max(Hitze_P1rc)), color = 'green') +
  geom_label(aes(y = 1.2, x = min(Hitze_P1rc), label = paste0('min = ',round(min(Hitze_P1rc),2)))) +
  xlab('Insert what your variable means here!') +
  theme_minimal() +
  theme(
    axis.title.y = element_blank(), 
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )+
theme_tufte()
```

```{r chord diagram}
# Create an adjacency matrix: 
# a list of connections between 20 origin nodes, and 5 destination nodes:
numbers <- sample(c(1:1000), 100, replace = T)
data <- matrix( numbers, ncol=5)
rownames(data) <- paste0("orig-", seq(1,20))
colnames(data) <- paste0("dest-", seq(1,5))

# Load the circlize library
library(circlize)
 
# Make the circular plot
chordDiagram(data, transparency = 0.5)


```

```{r chord diagram 2}
# Create an edge list: a list of connections between 10 origin nodes, and 10 destination nodes:
origin <- paste0("orig ", sample(c(1:10), 20, replace = T))
destination <- paste0("dest ", sample(c(1:10), 20, replace = T))

origin<-c("Linda","Svenja","Maria","Linda","Jürgen")
destination<-c("Andi","Ludwig","Jürgen","Svenja","Ludwig")
data <- data.frame(origin, destination)

# Transform input data in a adjacency matrix
adjacencyData <- with(data, table(origin, destination))
 
# Charge the circlize library
library(circlize)
 
# Make the circular plot
chordDiagram(adjacencyData, transparency = 0.5)
```