---
title: "IC_Map"
author: "Linda Menk"
date: "27 11 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(httr)
library(rlist)
library(jsonlite)
library(dplyr)
library(sf)
library(sp)
library(rgdal)
library(tmap)
library(RColorBrewer)
library(ggplot2)
library(ggthemes)
library(tidyverse)


World<-st_read("R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP1\\T1_3\\Manuscript\\Data\\ne_110m_admin_0_countries\\ne_110m_admin_0_countries.shp")


Names_1<-c("France","Slovakia","Portugal","Ukraine","Hungary","Uruguay","Mauritania","Ethiopia","Burundi","Somalia","Kenya","Nigeria","Ghana","Mali","Pakistan","Vietnam","Japan","Russia","China","South Korea")
Names_2<-c("Germany","Netherlands","Canada","India","Australia")
Names_3<-c("Spain","Austria","Brazil","United States of America")
Names_8<-c("United Kingdom")
  
World$count<-0
World$count[World$SOVEREIGNT %in% Names_1]<- 1
World$count[World$SOVEREIGNT %in% Names_2]<- 2
World$count[World$SOVEREIGNT %in% Names_3]<- 3
World$count[World$SOVEREIGNT %in% Names_8]<- 8

#st_write(World, dsn="C:/Users/b1019175/Documents/UNCHAIN_studyareas_test2.shp", driver="ESRI Shapefile", overwrite_layer = TRUE)


```

```{r map, fig.height=7, fig.width=9}

# Assign continent
Europe<-c("France","Slovakia","Portugal","Ukraine","Hungary","Germany","Netherlands","Spain","Austria","United Kingdom")
Africa<-c("Mauritania","Ethiopia","Burundi","Somalia","Kenya","Nigeria","Ghana","Mali")
Asia<-c("Pakistan","Vietnam","Japan","Russia","China","South Korea","India")
N.America<-c("United States of America","Canada")
S.America<-c("Brazil", "Uruguay")
Oceania<-c("Australia")

World$continent<-NULL
World$continent[World$SOVEREIGNT %in% Europe]<- "Europe"
World$continent[World$SOVEREIGNT %in% Africa]<- "Africa"
World$continent[World$SOVEREIGNT %in% Asia]<- "Asia"
World$continent[World$SOVEREIGNT %in% N.America]<- "N.America"
World$continent[World$SOVEREIGNT %in% S.America]<- "S.America"
World$continent[World$SOVEREIGNT %in% Oceania]<- "Oceania"

World$continent_nr<-NULL
World$continent_nr[World$SOVEREIGNT %in% Europe]<- 1
World$continent_nr[World$SOVEREIGNT %in% Africa]<- 2
World$continent_nr[World$SOVEREIGNT %in% Asia]<- 3
World$continent_nr[World$SOVEREIGNT %in% N.America]<- 4
World$continent_nr[World$SOVEREIGNT %in% S.America]<- 5
World$continent_nr[World$SOVEREIGNT %in% Oceania]<- 6

#Remove all other countries from the dataset
ed_exp4 <- subset(World, count != 0)


#Make dataframe from remaining countries
spatial<-data.frame("SOVEREIGNT"=ed_exp4$SOVEREIGNT, "count"=ed_exp4$count, "continent"=ed_exp4$continent, "cont_nr"=ed_exp4$continent_nr)
#Remove duplicates
spatial <- spatial[-c(10, 29), ]

#Europe & World
#Europe<-data.frame("Europe",3,"Overarching",7)
#names(Europe)<-c("SOVEREIGNT","count","continent","cont_nr")
#spatial<-rbind(spatial,Europe)

#Global<-data.frame("Global",3,"Overarching",7)
#names(Global)<-c("SOVEREIGNT","count","continent","cont_nr")
#spatial<-rbind(spatial,Global)

#Make the plot
map<-ggplot(spatial,aes(x=count, y=reorder(SOVEREIGNT, count), fill = continent))+geom_bar(stat="identity", width=0.7)+ggtitle("Assessment location")+xlab("")+ylab("")+
  scale_fill_wsj() +
  theme_fivethirtyeight() +
  facet_grid(spatial$cont_nr~., scales ="free",space="free")+
  labs(fill = " ") +
  theme(strip.text.y=element_blank())
  
map
```

```{r risk}

AR4<-"Vulnerability (Adaptive Capacity + \n Exposure + Sensitivity) + Hazard"
AR5<-"Vulnerability + \nExposure + \nHazard"
None<-"Other/\nNone mentioned"
NAP<-"Not applicable"
Oth<-"Other"

#Times risk concept
types_df<-data.frame(
  type=c(AR4, AR5, NAP, Oth, None),
  count=c(9,11,6,3,9)
  )

p<-ggplot(data=types_df, aes(x=count, y=type)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=count), vjust=1.6, color="white", size=3.5, nudge_x = -1)+
 ggtitle("Assessment scale")+xlab("Number of studies")+ylab(" ")
p

#Times per year
years_df<-data.frame(year=as.factor(c(2010,2011,2012,2013,2014,2015,2016,2017,2018,2019)),
                     times=c(1,0,1,2,5,5,4,2,13,5))
p<-ggplot(data=years_df, aes(x=year, y=times)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=times), vjust=1.6, color="white", size=3.5, nudge_x = 0,nudge_y=0)+
 ggtitle("Articles per year")+xlab("Number of articles")+ylab("Year")+theme_solarized() 
p

df <- data.frame(
  group = c(AR4, AR5, AR4, None, NAP, AR5, None, None, None, AR5, None, None, AR4, None, None, None, None, AR5, NAP, None, NAP, NAP, AR5, NAP, AR5, NAP, None, AR5, AR5, AR4, AR4, AR5, AR4, AR4, AR5, AR4, AR4, AR5),
  value = as.factor(c(2015, 2018, 2018, 2014, 2016, 2018, 2015, 2018, 2018, 2017, 2018, 2018, 2012, 2018, 2015, 2018, 2010, 2016, 2017, 2014, 2019, 2013, 2015, 2019, 2018, 2019, 2013, 2019, 2016, 2014, 2014, 2018, 2014, 2016, 2018, 2018, 2015, 2019))
  )
df

library(ggplot2)

theme_update(plot.title = element_text(hjust = 0.5))

#Risk conceptualisation plot
p<-ggplot(data=df, aes(x=value, y=group)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -1)+
 ggtitle("Risk conceptualisation")+xlab("Number of studies")+ylab(" ")
p



ggplot(df, aes(x = value)) +
    geom_bar(stat="count")
#-----------
tbl <- with(df, table(group,value))

df<-data.frame(tbl)

p<-ggplot(df,aes(factor(value), Freq, fill = group))+geom_bar()+ggtitle("Definitions over time")+xlab("Definition")+ylab("Usage per year")

p<-ggplot(df,aes(x = value, y = Freq, fill = group))+geom_bar(stat="identity", width=0.5)+ggtitle("Risk concepts and number of articles")+xlab(" ")+ylab("Number of articles")+
  scale_fill_wsj() +
  theme_fivethirtyeight() +
  labs(fill = "Risk concept")

p


# Stacked
ggplot(df, aes(fill=value, x=value)) + 
    geom_bar(position="stack", stat="identity", width = 1)
# Horizontal bar plot
#p + coord_flip()

```

```{r scale}
scale <- data.frame(
  group = c("Global","Continental","Multi-national","National","Sub-national","Urban area/City","Local","Infrastructure"),
  value = c(3,3,2,13,11,7,3,2)
  )

p<-ggplot(scale,aes(x=value, y=reorder(group,value)))+geom_bar(stat="identity", width=0.5)+ggtitle("Assessment scale")+xlab("Times mentioned")+ylab("")+
  scale_fill_wsj() +
  theme_fivethirtyeight() +
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -1, nudge_y = +0.3)

p
# Horizontal bar plot
#p + coord_flip()

```

```{r risk}
risk <- data.frame(
  group = c("Sensitivity, Adaptive capacity", "IPCC AR5/DRR","Not specified","Other"),
  value = c(8, 9, 16, 6)
  )
head(risk)

library(ggplot2)

theme_update(plot.title = element_text(hjust = 0.5))

p<-ggplot(data=risk, aes(x=value, y=group)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -1)+
 ggtitle("Conceptionalisation of risk")+xlab("Number of studies")+ylab(" ")
p


# Horizontal bar plot
#p + coord_flip()

```

```{r model}
model <- data.frame(
  group = c("Economic quantification", "Impact Chain","Network Analysis","SD/CLD/Scenario based","Other"),
  value = c(7, 12, 5, 7,8)
  )
head(model)

library(ggplot2)

theme_update(plot.title = element_text(hjust = 0.5))

p<-ggplot(data=model, aes(x=value, y=group)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -1)+
 ggtitle("Used modelling techniques")+xlab("Number of studies")+ylab(" ")
p


# Horizontal bar plot
#p + coord_flip()

```

```{r knowledge}
knowledge <- data.frame(
  group = c("Participatory (incl. expert opinion, \nstakeholder experience, surveys)", "Literature","Existing models","Statistical, quantitative \ndata analysis"),
  value = c(19, 17, 7, 17)
  )

p<-ggplot(knowledge,aes(x=value, y=group))+geom_bar(stat="identity", width=0.5)+ggtitle("Knowledge acquisition method")+xlab("Times mentioned")+ylab("")+
  scale_fill_wsj() +
  theme_fivethirtyeight() +
  geom_text(aes(label=value), vjust=1.6, color="white", size=3.5, nudge_x = -1, nudge_y = +0.18)

p
# Horizontal bar plot
#p + coord_flip()

```
```{r Treemap, fig.height=5}



hazard<-data.frame(names=c("Changed precipitation patterns",
                           "Changed temperature patterns",
                           "Rapid onset events",
                           "Heatwave",
                           "Cold spell",
                           "Sea Level Rise",
                           #"Coastal erosion",
                           "Storm surges/(Coastal) floods",
                           "Storm/wind, heavy precipitation, snow",
                           "(coastal) erosion/landslide",
                           "Water scarcity",
                           "Water quality deterioration",
                           "Salinization",
                           "Drought",
                           "Desertification/forest dieback",
                           "Overarching w/o specification"),
                   value=c(2,2,2,7,2,2,18,9,8,2,1,1,11,2,9),
                   level=as.character(c(20,20,10,1,1,2,0,0,0,1,1,0,1,1,5)))

#Make the plot
map<-ggplot(hazard,aes(x=value, y=reorder(names,value), fill=level))+geom_bar(stat="identity", width=0.7)+ggtitle("Assessed hazards/climate impacts")+xlab("")+ylab("")+
  scale_fill_wsj() +
  theme_fivethirtyeight() +
  facet_grid(hazard$level~., scales ="free",space="free")+
  labs(fill = " ") +
  theme(legend.position = "none",strip.text.y=element_blank())
  
map
```

```{r stef}
library(ggplot2)

#load polygons
library(sf)
Hitze_P1rcp45q05 <- st_read("R:\\02_PROJECTS\\01_P_330001\\PKF330001_02_HotSpots\\01_Data\\Daten-vom-20201013\\Hotspots_Karten\\Index_shapefiles\\Hitzebelastung_P1rcp45q05_SmoothSBG_1.shp")
plot(Hitze_P1rcp45q05)
Hitze_P1rcp45q05_density <- density(Hitze_P1rcp45q05$Hitze_P1rc)
plot(Hitze_P1rcp45q05_density)

ggplot(Hitze_P1rcp45q05) +
  geom_density(aes(Hitze_P1rc)) +
  geom_vline(aes(xintercept = min(Hitze_P1rc)), color = 'red') +
  geom_vline(aes(xintercept = mean(Hitze_P1rc)), color = 'blue') +
  geom_vline(aes(xintercept = max(Hitze_P1rc)), color = 'green') +
  geom_label(aes(y = 1.2, x = min(Hitze_P1rc), label = paste0('min = ',round(min(Hitze_P1rc),2)))) +
  xlab('Insert what your variable means here!') +
  theme_minimal() +
  theme(
    axis.title.y = element_blank(), 
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )+
theme_tufte()
```
```

```{r chord diagram}
# Create an adjacency matrix: 
# a list of connections between 20 origin nodes, and 5 destination nodes:
numbers <- sample(c(1:1000), 100, replace = T)
data <- matrix( numbers, ncol=5)
rownames(data) <- paste0("orig-", seq(1,20))
colnames(data) <- paste0("dest-", seq(1,5))

# Load the circlize library
library(circlize)
 
# Make the circular plot
chordDiagram(data, transparency = 0.5)


```

```{r chord diagram 2}
# Create an edge list: a list of connections between 10 origin nodes, and 10 destination nodes:
origin <- paste0("orig ", sample(c(1:10), 20, replace = T))
destination <- paste0("dest ", sample(c(1:10), 20, replace = T))

origin<-c("Linda","Svenja","Maria","Linda","Jürgen")
destination<-c("Andi","Ludwig","Jürgen","Svenja","Ludwig")
data <- data.frame(origin, destination)

# Transform input data in a adjacency matrix
adjacencyData <- with(data, table(origin, destination))
 
# Charge the circlize library
library(circlize)
 
# Make the circular plot
chordDiagram(adjacencyData, transparency = 0.5)
```